% File: main.tex
\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
\usepackage[submission]{aaai2026}  % DO NOT CHANGE THIS
\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS

% (Optional helpers; remove if not needed)
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off}
\lstset{basicstyle={\footnotesize\ttfamily},numbers=left,numberstyle=\footnotesize,
xleftmargin=2em,aboveskip=0pt,belowskip=0pt,showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}

\pdfinfo{
/TemplateVersion (2026.1)
}

\setcounter{secnumdepth}{0}

% ---------------- Title / Authors ----------------
\title{Project Proposal (Max 2 Pages)\\
Reproduction Plan: \emph{[Insert Paper Title Here]}}
\author{Anonymous Submission}
\affiliations{~}

\begin{document}
\maketitle

\begin{abstract}
[One–to–three sentence overview of your reproduction plan.]
\end{abstract}

% =========================================================
\section{Introduction (3)}
[Motivate the problem and why reproducing this paper matters; state your goals and what you will verify.]


% =========================================================
\section{Problem Statement (2)}
\textbf{What is the problem statement of the paper you are proposing to reproduce?}

[One to two precise sentences.]


% =========================================================
\section{Citation to the Original Paper (1)}
[Full citation with authors, title, venue/year, DOI/URL or arXiv.]

% =========================================================
\section{Methodology (6)}

\subsection{Specific Approach (2)}
\textbf{What was the specific approach they took to solve the problem? Include models, techniques, and evaluation metrics.}

\textit{Models:} [Teacher / Student backbones] \\
\textit{Techniques:} [e.g., KD variants, uncertainty handling, contrastive loss, aggregation rule] \\
\textit{Evaluation metrics:} [Accuracy, Specificity, Sensitivity, AUC, etc.]

\subsection{Novelty / Relevance / Hypotheses to be Tested (2)}
\textbf{What exactly is the novelty or relevance of their paper? Why is their proposed method better than baselines? What hypothesis do they make?}

[Summarize contributions; why it beats baselines; list explicit hypotheses (H1, H2, ...).]

\subsection{Ablations / Extensions Planned (2)}
\textbf{What do you think could improve their method? Is their hypothesis legitimate?}

[Planned ablation bullets; proposed extensions; how you will test hypothesis legitimacy.]

% =========================================================
\section{Data Access and Implementation Details (5)}

\subsection{Description of How You Will Access the Data/Model (2)}
\textbf{What is the dataset they use and do they use a public codebase?}

[Dataset name(s), access path (public/credentialed), any open-source repo or demo, and your access plan.]


\subsection{Discussion of the Feasibility of the Computation (2)}
[Compute budget (GPUs/CPUs/RAM), expected training time, storage, libraries, risks and mitigations.]

We will be using 

\subsection{Statement of Whether You Will Use the Existing Code or Not (1)}
[Explicitly: use existing code / partial reuse / reimplement. Brief justification.]

\subsection{The Project Proposal Is Within 2 Page Limit (1)}
[Affirmation: This document is $\leq$ 2 pages in AAAI submission format.]

% =========================================================
\section{Additional Comments or Insights on Using LLM Prompts}
\textit{How did you tweak the prompt to be more effective/useful?}

[Brief notes: structure, constraints, request citations/sections, require bullet points, etc.]

% ---------------- References / Appendix (Unlimited) ----------------
% If you have aaai2026.bst and refs.bib in your project, uncomment the next line:
% \bibliography{refs}

% Otherwise, use a manual placeholder (delete once BibTeX is set up):
% \small
% \noindent\textbf{References (placeholder)}\quad [Add your references or enable BibTeX.]

\end{document}
